### 2016-03-06 paper/introduction.tex
yasu

\section{Introduction}
Parallel computation has changed the field of Computing.  In the 90s,
most processors had single cores. In 2016, most processors have multiple
cores, often 4 or even 8. Cluster computing further expands the
potential of parallel computation, where one can easily launch a
processing job using hundreds or even thousands of computers in a
cloud. Computer Vision is not an exception in exploiting the powerful
parallel computation. However, in many Computer Vision problems,
state-of-the-art algorithms are still inherently sequential. Take a
Fusion-Move algorithm (FM)~\cite{viktor,second_order_stereo,else} for
example. FM was first introduced by Lempitsky et al. in solving an
optical flow problem. FM allows one to customize domain-specific
proposal generation schemes to achieve efficient convergence. FM has
been a very successful optimization framework in solving many
challenging problems in Computer Vision such as optical flow, stereo,
image denoising, image inpainting, or image
segmentation~\cite{fusion_moves_for_markov_random_field_optimization}. The
main limitation of FM is its running time, where Computer Vision
researchers and engineers generally consider FM to be a slow algorithm
that can solve challenging problems by fusing hundreds or sometimes
thousands of proposals sequentially.
%
The running time becomes particularly an issue for large

image denoising for high resolution images (24mb), high resolution
map-tile image stitching (satellite), voxel CRF~\cite{pollefeys}

\yasu{Are there any concrete examples where MRF is used to solve a very
large problem where parallel fusion is really helpful. Like denoising
high resolution 24M pixel images. Stitching a high resolution map tiles
(satellite image tiles) via image stitching.}

%
This paper will propose a {\it Parallel Fusion Move} (PFM) method that
introduces the concept of parallel fusion into the computational
framework.

FM suffers from a few fundamental limitations due to its sequential
nature. First, standard FM offers only two options in each fusion,
either the current solution or a single proposal. Recently, an extension
of FM was proposed for layered depthmap estimation~\cite{chen_2016},
where a solution subspace, instead of a single solution, is proposed
from each proposal generation scheme. However, a solution is
sequentially updated by a single generation scheme one by one. In our
framework, multiple threads (or computing nodes) simultaneously keep and
improve solutions. Furthermore, in each fusion step in each thread, our
approach can take any number of proposals from any number of proposal
generation schemes, and even concurrent solutions in the other threads
to fuse them into a new solution.
%
Note that one can seek to parallelize the core optimization libraries
such as Graph-cuts~\cite{}, TRW~\cite{kolmogorov}, or QPBO~\cite{} to
achieve similar speed-up. However, these core optimization libraries are
often very complicated and used as a complete black box. Some libraries
are provided only in a binary form, especially commercial
packages. Furthermore, this library modification cannot benefit from
higher level parallelism through distributed computer nodes.
\yasu{Mention that existing fm only does binary solution fusion. We does
multi-solution fusion. This overlaps withour cvpr16, but is probably ok
by citing the paepr.}
%
The idea in this paper is extremely simple and easily reproducible. This
paper can instantly benefit every Computer Vision researcher or
engineer, who currently uses fusion move algorithm to solve challenging
problems. We will share our implementation of the algorithm. The rest of
the paper is organized as follows. Section~\ref{section:related_work}....
%This paper will propose a novel Parallel Fusion
%Move method, which fuses solution proposals in parallel. Our framework
%can exploit parallelism from the levels of threading to the levels of
%computer nodes.
%
 \yasu{Hopefully, more interesting things will come up through
experiments and we have more to say. For example, it would be cool if
uniform model is better than pure master-slave. Then we can write that
ours is not just parallel. But keeping multiple solutions somehow
benefit (GA/GP algorithm's ideas).}

>>>>

\section{Introduction}
Parallel computation has changed the field of Computing.  In the 90s,
most processors had single cores. In 2016, most processors have multiple
cores, often 4 or even 8. Cluster computing further expands the
potential of parallel computation, where one can easily launch a
processing job using hundreds or even thousands of computers in a
cloud.
%
Parallel computation offers huge potential for Computer Vision, as
image sensing technologies have gone through revolutions and we are in
ever growing demands in solving very large problems. One may need to
apply image denoising to 50 Megapixel images from latest digital
SLRs~\cite{canon?}, stitch thousands of images to generate gigapixel
panoramas~\cite{gigapan}, or solve volumetric reconstruction and
segmentation problems over a billion ($=1024^3$)
voxels~\cite{Joint_3D_Scene_Reconstruction_and_class_Segmentation}.

Unfortunately, in many Computer Vision problems, state-of-the-art
algorithms are still inherently sequential. Take a Fusion-Move algorithm
(FM)~\cite{viktor,second_order_stereo,else} for Markov Random Field
inference, for example, which has been one of the most effective
techniques in solving the above three
problems~\cite{fusion_moves_for_markov_random_field_optimization}.
%
FM was first introduced by Lempitsky et al. in solving an optical flow
problem, where solution proposals are fused sequentially one by one to
improve the solution. FM allows domain-specific customization of
proposal generation schemes, a main advantage over general solvers such
as message passing algorithms~\cite{TRW,loopy_belief_propagation}. FM
has been successful applied to many challenging problems in optical
flow, stereo, image denoising, image inpainting, or image
segmentation~\cite{fusion_moves_for_markov_random_field_optimization}.

Breaking the sequential nature of FM would then bring fundamental
contributions to many major fields in Computer Vision. FM suffers from a
few vital limitations due to its sequential processing. First, standard
FM allows only two options per variable in each fusion, either the
current solution or a
proposal~\cite{fusion_moves_for_markov_random_field_optimization}.
Recently, an extension of FM was proposed for layered depthmap
estimation~\cite{chen_2016}, where a solution subspace, instead of a
single solution, is proposed and fused with the current
solution. However, existing approaches use only one proposal generation
scheme in each fusion.

Our approach, dubbed {\it Parallel Fusion Move Method} (PFM), makes a
few key distinctions from existing approaches: 1) Multiple threads (or
computing nodes) simultaneously keep and improve solutions; and 2) Each
fusion in each thread can take arbitrary number of proposals from
arbitrary combination of proposal generation schemes, even concurrent
solutions in the other threads, to be fused with the current solution.
%
Note that one may rather seek to parallelize the core optimization
libraries such as Graph-cuts~\cite{}, TRW~\cite{kolmogorov}, or
QPBO~\cite{}.~\footnote{GPU speeds-up message-passing algorithms via
parallel computation. However, these algorithms need to store all the
messages and states and cannot handle problems with a large label space~\cite{layered_depthmap}.} However, the core optimization libraries are often
very complex and require significant engineering by experts for
modification.
%
While state-of-the-art optimization libraries are often freely available for
non-commercial purposes, most companies have to develop and maintain
in-house implementation of these optimization algorithms.
%
% \yasu{Mention that existing fm only does binary solution fusion. We does
% multi-solution fusion. This overlaps withour cvpr16, but is probably ok
% by citing the paepr.}
%
Our approach is extremely simple in concept, and will instantly benefit
every Computer Vision researcher or engineer, who currently uses fusion
move algorithm to solve challenging problems. We will share our
implementation of the algorithm. The rest of the paper is organized as
follows. Section~\ref{section:related_work}....
%This paper will propose a novel Parallel Fusion
%Move method, which fuses solution proposals in parallel. Our framework
%can exploit parallelism from the levels of threading to the levels of
%computer nodes.

%The main limitation of FM is its running time, where Computer Vision
%researchers and engineers generally consider FM to be a slow algorithm
%that can solve challenging problems, as hundreds or sometimes thousands
%of proposals need to be fused sequentially.
%

%\yasu{Are there any concrete examples where MRF is used to solve a very
%large problem where parallel fusion is really helpful. Like denoising
%high resolution 24M pixel images. Stitching a high resolution map tiles
%(satellite image tiles) via image stitching.}

%
%This paper will propose a {\it Parallel Fusion Move} (PFM) method that
%introduces the concept of parallel fusion into the computational
%framework.

%
 \yasu{Hopefully, more interesting things will come up through
experiments and we have more to say. For example, it would be cool if
uniform model is better than pure master-slave. Then we can write that
ours is not just parallel. But keeping multiple solutions somehow
benefit (GA/GP algorithm's ideas).}

%\yasu{mention GPU somewhere? strange to talk about parallel without
%mentioning GPU and its relation to our approach}
